\chapter{Introduction}
\label{sec:introduction}
This chapter will introduce the subject of mixed criticality embedded systems and the project EMC2 to the reader.

\section{Background}
Today, modern automotive systems contain a large number of Electronic Control Units (ECU)s \cite{}, each controlling a specific system of a specific criticality level such as safety-critical anti-lock brake system or non-critical entertainment systems \cite{}. %This approach provides isolation for the numerous critical and non-critical applications in the collective system, and a simple mechanism to qualify an individual ECU. However, it yields an inefficient and expensive system implementation. In order to lower the cost of the system and increase performance, mixed-criticality applications can be integrated into a single multicore platform. This solution will reduce the number of ECUs in the system, which in turn lowers the manufacturing and maintenance costs [6]. Combining applications into a single multicore platform can greatly increase performance and reduce cost. However, this approach increases system complexity, and hinders the certification of safety-critical systems [3]. In order to facilitate the design, test, and certification of such systems, spatial and temporal partitioning can be used in the architecture of the system.

\subsection{Definition of safety-critical systems}
A safety critical system is defined as "A computer, electronic or electromechanical system whose failure may cause injury or death to human beings", as described by \cite{}.

\section{Problem statement}
Implement safety-critical controller on the embedded system.

\subsection{Research question}
How well can a safety-critical control system perform when implemented on a mixed criticality system using virtualization?

\section{Purpose}
In order to reduce the amount of ECUs in mechatronic systems, it must be verified that non safety critical applications do not interfere with safety critical applications.

\section{Goals}
In this project there are both team goals and individual goals that do not necessarily align with each other.

\subsection{Team goal}
Team demonstrator

\subsection{Individual goal}
Verify quantitatively the performance of safety-critical controller.

\subsection{Scope}
The thesis is produced at Alten.
Constrained to the Xilinx Zynq-7000 \footnote{https://www.xilinx.com/products/silicon-devices/soc/zynq-7000.html}.

\subsection{Method}
Implement safety-critical controller on the embedded system. Measure performance of controller. Missed deadlines? CPU usage? Compare with no non safety-critical load.